---
title: "knitr report for a drake plan"
author: "you"
date: "August 18, 2018"
output: html_document
---

Visit https://ropenscilabs.github.io/drake-manual/plans.html to learn about workflow plan data frames in drake.

You can use a `knitr` report with code chunks to create a `drake` plan. Here is a target and its command.

```{r chunk}
data1 <- rnorm(10)
```

You can use various assignment operators.

```{r names}
data2 <<- rnorm(20)
```

Assignment operators can go either way.

```{r are}
mean(data1) -> summary1
median(data2) ->> summary2
```

You can assign triggers, etc. in the same way you would in `drake_plan()`.

```{r not}
discrepancy <- target(
  command = summary2 - summary1,
  trigger = trigger(condition = TRUE),
  timeout = 100
)
```

But each target can take only one expression as its command. Please enclose multiple lines in curly braces.

```{r important}
sum1 = {
  tmp <- 0
  for (i in 1:10){
    tmp <- tmp + data1[i]
  }
  tmp
}

{
  tmp <- 0
  for (i in 1:10){
    tmp <- tmp + data2[i]
  }
  tmp
} -> sum2
```

Unevaluated/inactive code chunks are ignored.

```{r here, eval = FALSE}
print("not run")
```
